CSci487 Penetration Testing Project: AILEE

### 2019-05-05 csci487/project/paper.tex
Remove broken quotes, update paragraph on ls command to include colors
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\graphicspath{ {./} }
\usepackage{listings}
\usepackage{color}

@@

@@

\lstset{style=mystyle}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

The directories are colored light blue, executable files are colored light green and all have a .exe extension, and regular files are colored white and must have a .something extension (Fig. 5). One difference between AILEE and a real-life Linux terminal is that the \textit{ls} command cannot be given an argument in the game, and thus can only be used in the current directory.

@@

\begin{thebibliography}{00}
\bibitem{b1} Repl.it, “The world's leading online coding platform,” repl.it. [Online]. Available: https://repl.it/site/features. [Accessed: 02-May-2019].

\bibitem{b2} A. M. Kuchling and E. S. Raymond, “Curses Programming with Python¶,” Curses Programming with Python - Python 3.7.3 documentation. [Online]. Available: https://docs.python.org/3/howto/curses.html. [Accessed: 02-May-2019].

\end{thebibliography}

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{float}
\graphicspath{ {./} }
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}

@@

% came from the ANSI escape sequence color table as implemented by Ubuntu
% used for colorizing the ls-description paragraph
\definecolor{folder-blue}{RGB}{0,111,184}
\definecolor{file-green}{RGB}{57,181,74}

@@

\lstset{style=mystyle}

% what does this do?  i commented it out and can't tell any difference -misha
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

@@

Directories are colored \textcolor{folder-blue}{\textbf{light blue}}, executables a \textcolor{file-green}{\textbf{light green}}, and regular files are white.  Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.  However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.

@@

\begin{thebibliography}{00}
\bibitem{b1} Repl.it, ``The world's leading online coding platform,'' repl.it. [Online]. Available: \url{https://repl.it/site/features}. [Accessed: 02-May-2019].

\bibitem{b2} A. M. Kuchling and E. S. Raymond, ``Curses Programming with Python,'' Curses Programming with Python - Python 3.7.3 documentation. [Online]. Available: \url{https://docs.python.org/3/howto/curses.html}. [Accessed: 02-May-2019].
\end{thebibliography}
